---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# wtfismyip

A simple, dependency free wrapper around [wtfismyip](https://wtfismyip.com/).

## How to

Just : 

```{r results='hide'}
wtfismyip::wtfismyip()
```

## Get verbose

If you want the function to get verbose : 

```{r results='hide'}
wtfismyip::wtfismyip(verbose = TRUE)
```

Returns you a dataframe with : 

+ IP Address 
+ Location
+ Hostname
+ ISP
+ TorExit 
+ Country code

## Get polite

If you don't want to know what is YourFuckingIPAddress but simply what is your IPAddress, pass the `polite = TRUE` argument : 

```{r results='hide'}
wtfismyip::wtfismyip(verbose = TRUE, polite = TRUE)
```

### Contact

Questions and feedbacks [welcome](mailto:contact@colinfay.me)!

You want to contribute ? Open a [PR](https://github.com/ColinFay/wtfismyip/pulls) :) If you encounter a bug or want to suggest an enhancement, please [open an issue](https://github.com/ColinFay/wtfismyip/issues).
